---
title: "Classification"
toc: true
toc-depth: 6
execute:
  echo: false
  message: false
  warning: false
---

```{r}
#| include: false
release <- jsonlite::fromJSON(
  "https://api.github.com/repos/pteridogroup/ppg/releases/latest"
)
tag <- release$tag_name

# Concept DOI 10.5281/zenodo.22760360 covers all versions of the PPG
# Zenodo record; look up the specific version whose DOI matches this
# release (falling back to the most recently published version if none
# matches, e.g. due to sync lag between GitHub and Zenodo).
zenodo_versions <- jsonlite::fromJSON(
  "https://zenodo.org/api/records?q=conceptrecid:22760360&all_versions=true"
)$hits$hits

match_idx <- which(zenodo_versions$metadata$version == tag)
zenodo <- if (length(match_idx) > 0) {
  zenodo_versions[match_idx[1], ]
} else {
  zenodo_versions[which.max(as.Date(zenodo_versions$metadata$publication_date)), ]
}
```

This classification below is PPG `r tag` ([DOI: `r zenodo$doi`](`r zenodo$links$doi`)) and only shows accepted names at the rank of genus and higher. See the [Project Guidelines](guidelines.qmd#versioning) for details on versioning.

To see details such as species-level names, synonyms, etc., please browse the data using the [PPG Database Viewer](dataviewer.qmd). You may also access the data through [Rhakhis](https://list.worldfloraonline.org/rhakhis) (live data) or [World Flora Online (WFO)](https://wfoplantlist.org) (biannual snapshots).
For more information about WFO, see [here](wfo.qmd).

```{r}
#| results: asis
lines <- readr::read_lines(
  glue::glue(
    "https://raw.githubusercontent.com/pteridogroup/ppg/refs/tags/{tag}/data/ppg.md"
  )
)

lines <- lines[lines != "# PPG"]

cat(lines, sep = "\n\n")
```